Plot responses to model covariates to inform threshold choices for VOCC

### 2019-10-02 analysis/VOCC/3-fixed-var-response-plots.Rmd
remove root lines for increasing DO and decreasing temp; change binning for raw density plots

Species
```{r}

# # Species run so far...
# species <- "Arrowtooth Flounder" # temp good, not DO, imm moving deeper?

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- paste0(x2016,covs) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- exp(roots[["optimal"]])
   do[[i]]$lower_do_50 <- exp(roots[["lower_threshold"]])
   do[[i]]$upper_do_50 <- exp(roots[["upper_threshold"]])
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- exp(roots75[["lower_threshold"]])
   do[[i]]$upper_do_75 <- exp(roots75[["upper_threshold"]])
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- exp(roots25[["lower_threshold"]])
   do[[i]]$upper_do_25 <- exp(roots25[["upper_threshold"]])
   do[[i]]$x <- exp(do[[i]]$x)
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0.2, 8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=(do[[i]]$optimal_do), size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=(do[[i]]$lower_do_50), linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=(do[[i]]$upper_do_50), linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=(do[[i]]$lower_do_75), linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=(do[[i]]$upper_do_75), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$lower_do_25), linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=(do[[i]]$upper_do_25), linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

#### Calculate temperature curves
```{r}
td <- list()
temp_plots <- list()
for (i in seq_len(length(model_list))) {
 if(model_list[[i]]$model$convergence==0){
  td[[i]] <- fixed_density(model_list[[i]], predictor = "temp", quadratics_only = FALSE, fixed_params = num_params)
  if (length(td[[i]])>0) {
    td[[i]]$species <- species
    td[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
    td[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
    td[[i]]$model <- names(model_list[i])
    td[[i]]$covs <- paste0(x2016,covs) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.5)
   td[[i]]$optimal_temp <- roots[["optimal"]]
   td[[i]]$lower_t_50 <- roots[["lower_threshold"]]
   td[[i]]$upper_t_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.75)
   td[[i]]$lower_t_75 <- roots75[["lower_threshold"]]
   td[[i]]$upper_t_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.25)
   td[[i]]$lower_t_25 <- roots25[["lower_threshold"]]
   td[[i]]$upper_t_25 <- roots25[["upper_threshold"]]
   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 12)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5)

@@

#### Plot raw DO
```{r}
if(!is.null(data$adult_density)){
odata <- data %>% filter(!is.na(do_mlpl)) %>% 
  mutate(ad_density_class = ifelse(adult_density==0, 0, (round(log10((adult_density*10000)+1)*2)+1)),
    im_density_class = ifelse(imm_density==0, 0, (round(log10((imm_density*10000)+1)*2)+1))) %>% 
  group_by(ad_density_class) %>% mutate(ad_mean_density = mean(adult_density, na.rm = TRUE)) %>% ungroup() %>%
  group_by(im_density_class) %>% mutate(im_mean_density = mean(imm_density, na.rm = TRUE)) %>% ungroup()

@@

#### Plot raw temperature
```{r}
if(!is.null(data$adult_density)){
tdata <- data %>% filter(!is.na(temp)) %>% 
  mutate(ad_density_class = ifelse(adult_density==0, 0, (round(log10((adult_density*10000)+1)*2)+1)),
    im_density_class = ifelse(imm_density==0, 0, (round(log10((imm_density*10000)+1))+1)*2)) %>% 
  group_by(ad_density_class) %>% mutate(ad_mean_density = mean(adult_density, na.rm = TRUE)) %>% ungroup() %>%
  group_by(im_density_class) %>% mutate(im_mean_density = mean(imm_density, na.rm = TRUE)) %>% ungroup()

@@

t_count_ad <- ggplot(tdata, aes(x = temp, stat(count),fill = as.factor(ad_density_class))) + 
  geom_density(position = "stack") +
  scale_fill_viridis_d(name = "Mean Density \n(kg/ha)", label=ad_density_class_labs) + 
  geom_vline(xintercept=tdat[tdat$model =="adult", ]$optimal_temp, color="black",  size=1, na.rm = TRUE) +
  geom_vline(xintercept=tdat[tdat$age =="adult", ]$optimal_temp, color="black", linetype="dashed", size=0.5, na.rm = TRUE) +
  theme_pbs() +
  xlab("Temperature from CTD") +
  ylab("Count") +
  ggtitle(paste("Adult", species))

t_prop_ad <- ggplot(tdata, aes(x = temp, stat(count), fill = as.factor(ad_density_class))) +
  geom_density(position = "fill") +
  scale_fill_viridis_d(name = "Mean Density \n(kg/ha)", label=ad_density_class_labs) + 
  geom_vline(xintercept=tdat[tdat$model =="adult", ]$optimal_temp, color="black", size=1, na.rm = TRUE) +
  geom_vline(xintercept=tdat[tdat$age =="adult", ]$optimal_temp, color="black", linetype="dashed", size=0.5, na.rm = TRUE) +
  theme_pbs() +
  xlab("Temperature from CTD") +
  ylab("Proportion") +
  ggtitle(paste("Adult", species))

>>>>

Species
```{r}
# # Species run so far...
# species <- "Arrowtooth Flounder" # temp good, not DO, imm moving deeper?

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- paste0(x2016,covs) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- exp(roots[["optimal"]])
   do[[i]]$lower_do_50 <- exp(roots[["lower_threshold"]])
   do[[i]]$upper_do_50 <- exp(roots[["upper_threshold"]])
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- exp(roots75[["lower_threshold"]])
   do[[i]]$upper_do_75 <- exp(roots75[["upper_threshold"]])
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- exp(roots25[["lower_threshold"]])
   do[[i]]$upper_do_25 <- exp(roots25[["upper_threshold"]])
   do[[i]]$x <- exp(do[[i]]$x)
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0.2, 8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=(do[[i]]$optimal_do), size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=(do[[i]]$lower_do_50), linetype="longdash", alpha = 0.75) + 
        #geom_vline(xintercept=(do[[i]]$upper_do_50), linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=(do[[i]]$lower_do_75), linetype="dotted", alpha = 0.5) + 
        #geom_vline(xintercept=(do[[i]]$upper_do_75), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$lower_do_25), linetype="dotted", alpha = 0.5) #+ 
        #geom_vline(xintercept=(do[[i]]$upper_do_25), linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

#### Calculate temperature curves
```{r}
td <- list()
temp_plots <- list()
for (i in seq_len(length(model_list))) {
 if(model_list[[i]]$model$convergence==0){
  td[[i]] <- fixed_density(model_list[[i]], predictor = "temp", quadratics_only = FALSE, fixed_params = num_params)
  if (length(td[[i]])>0) {
    td[[i]]$species <- species
    td[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
    td[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
    td[[i]]$model <- names(model_list[i])
    td[[i]]$covs <- paste0(x2016,covs) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.5)
   td[[i]]$optimal_temp <- roots[["optimal"]]
   td[[i]]$lower_t_50 <- roots[["lower_threshold"]]
   td[[i]]$upper_t_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.75)
   td[[i]]$lower_t_75 <- roots75[["lower_threshold"]]
   td[[i]]$upper_t_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.25)
   td[[i]]$lower_t_25 <- roots25[["lower_threshold"]]
   td[[i]]$upper_t_25 <- roots25[["upper_threshold"]]
   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 12)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") + 
        #geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        #geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        #geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5)

@@

#### Plot raw DO
```{r}
if(!is.null(data$adult_density)){
odata <- data %>% filter(!is.na(do_mlpl)) %>% 
  mutate(ad_density_class = ifelse(adult_density==0, 0, round(log10((adult_density*100000)+1))),
    im_density_class = ifelse(imm_density==0, 0, round(log10((imm_density*10000000)+1)))) %>% 
  group_by(ad_density_class) %>% mutate(ad_mean_density = mean(adult_density, na.rm = TRUE)) %>% ungroup() %>%
  group_by(im_density_class) %>% mutate(im_mean_density = mean(imm_density, na.rm = TRUE)) %>% ungroup()

@@

#### Plot raw temperature
```{r}
if(!is.null(data$adult_density)){
tdata <- data %>% filter(!is.na(temp)) %>% 
  mutate(ad_density_class = ifelse(adult_density==0, 0, round(log10((adult_density*100000)+1))),
    im_density_class = ifelse(imm_density==0, 0, round(log10((imm_density*10000000)+1)))) %>% 
  group_by(ad_density_class) %>% mutate(ad_mean_density = mean(adult_density, na.rm = TRUE)) %>% ungroup() %>%
  group_by(im_density_class) %>% mutate(im_mean_density = mean(imm_density, na.rm = TRUE)) %>% ungroup()

@@

t_count_ad <- ggplot(tdata, aes(x = temp, stat(count),fill = as.factor(ad_density_class))) + 
  geom_density(position = "stack") +
  scale_fill_viridis_d(name = "Mean Density \n(kg/ha)", label=ad_density_class_labs, begin=0, end=0.5) + 
  geom_vline(xintercept=tdat[tdat$model =="adult", ]$optimal_temp, color="black",  size=1, na.rm = TRUE) +
  geom_vline(xintercept=tdat[tdat$age =="adult", ]$optimal_temp, color="black", linetype="dashed", size=0.5, na.rm = TRUE) +
  theme_pbs() +
  xlab("Temperature from CTD") +
  ylab("Count") +
  ggtitle(paste("Adult", species))

t_prop_ad <- ggplot(tdata, aes(x = temp, stat(count), fill = as.factor(ad_density_class))) +
  geom_density(position = "fill") +
  scale_fill_viridis_d(name = "Mean Density \n(kg/ha)", label=ad_density_class_labs, begin=0, end=0.5) + 
  geom_vline(xintercept=tdat[tdat$model =="adult", ]$optimal_temp, color="black", size=1, na.rm = TRUE) +
  geom_vline(xintercept=tdat[tdat$age =="adult", ]$optimal_temp, color="black", linetype="dashed", size=0.5, na.rm = TRUE) +
  theme_pbs() +
  xlab("Temperature from CTD") +
  ylab("Proportion") +
  ggtitle(paste("Adult", species))
